\documentclass{weeklyreport}
\usepackage[utf8]{inputenc}

%%% Template Usage
% 1. Go to "All Projects" and make a copy in Overleaf,
% or download the source to modify locally.
% 2. Fill in your name
% 3. Set the reportdate to Monday of the current week


\title{Progress Report}
\author{Edris Qarghah}

\DTMsavedate{reportdate}{2020-07-27}
\date{Week of \DTMusedate{reportdate}}

\begin{document}

\maketitle

\newpage

\section*{Weekly Goals}


\begin{itemize}
	\item Learn about tomography strategies.
	\item Develop tomography of static network (e.g., with latency/packet loss).
	\item Ensure perfSONAR node distribution allows visibility into entire network.
	\item Generate, store and draw shortest paths between PS nodes.
	\item Stretch: Simulate network activity.
	\item Stretch: Generate time series data based on that activity.
	\item Stretch: Learn how this connects to anomaly detection.
	\item Stretch: Explore how the model can be applied to real network data.
\end{itemize}

\section*{Daily Log}

\subsection*{\weekday{0}}

\begin{itemize}
    \item Network Analytics Discussion meeting.
    \item Spoke with Ilija about using latency and hop distributions to tune packet loss so that it is appropriate for the scale of the model.
    \begin{itemize}
    	\item PS Nodes: 10 (model), 250 (real)
    	\item Nodes: 100 (model), 10000 (real)
    \end{itemize}
    \item Switched betweenness algorithms, per a suggestion from Andrew, dramatically increasing the speed of PerfSONAR node assignment.
\end{itemize}



\subsection*{\weekday{1}}

\begin{itemize}
    \item Created tables in Kibana to get latency (using one way delay) and hops (using trace), exported that data and added it to my project.
    \item Wrote functions to add and remove perfsonar nodes from existing graphs.
    \item Changed all nodes to text.
    \item Broke graphs because nearest distance tables relied on integer indexing.
\end{itemize}

\subsection*{\weekday{2}}

\begin{itemize}
    \item Fixed graphs by implementing consistent storage of nodes as strings and conversion to ints where necessary.
    \item Added versioning to graphs.
    \item Added save graph feature for modified graphs.
    \item Added functions to change perfsonar nodes
\end{itemize}

\subsection*{\weekday{3}}

\begin{itemize}
	\item SAND informal working meeting
    \item Tweaked edges to find
    \item Factored out edge creation to allow more control
    \item 
\end{itemize}


\subsection*{\weekday{4}}

\begin{itemize}
	\item Finished reports.
	\item 
\end{itemize}

\section*{Achievements}
\subsection*{I learned about...}
\begin{itemize}
	\item 
\end{itemize}

\subsection*{I created...}
\begin{itemize}
	\item 

\end{itemize}

\pagebreak
\section*{Roadblocks}

\subsection*{Questions}

\begin{itemize}
	\item 
\end{itemize}

\subsection*{Problems}

\begin{itemize}
	\item 
\end{itemize}

\subsection*{Challenges}

\begin{itemize}
    \item 
\end{itemize}

\section*{Plans for Next Week}

\begin{itemize}
	\item 
\end{itemize}

\end{document}
